Injury Outcomes

### 2023-12-11 injury_tables.Rmd
Updated function documentation, minor changes

### - output .csv files containing the following information:

@@

# - The inj_data.xlsx file (results/multi_city/inj/inj_data.xlsx) contains all injury output csv files

>>>>

### - output .csv files containing the following information. (Note this files are also saved with their output_version in the file name):

@@

# - The inj_data_*output_version*.xlsx file (results/multi_city/inj/inj_data_*output_version*.xlsx) contains all injury output csv files
